\documentclass[manual-fr.tex]{subfiles}
\begin{document}

\begin{itemize}
    \item[] \textbf{description}
        \begin{itemize}
            %\item[] Calcule la f-mesure sur des données étiquetées selon un schéma BIO. Fournit une f-mesure par classe, une micro f-mesure globale et une macro f-mesure globale.
            \item[] Compute the f-score over data tagged using IOB scheme. Gives f-score over each class, a micro- and a macro- global f-score.
        \end{itemize}
    \item[] \textbf{arguments}
        \begin{itemize}
            \item[] infile
                \begin{itemize}
                    \item[] The input file. Should follow the CoNLL format.
                \end{itemize}
        \end{itemize}
    \item[] \textbf{options}
        \begin{itemize}
            \item[] --help ou -h: switch
                \begin{itemize}
                    \item[] displays help
                \end{itemize}
            \item[] --reference-column ou -r: int
                \begin{itemize}
                    \item[] the index of the column where reference tags are located (default: -2).
                \end{itemize}
            \item[] --tagging-column ou -t: int
                \begin{itemize}
                    \item[] the index of the column where hypothesis tags given by the system are located (default: -1).
                \end{itemize}
            \item[] --input-encoding: string
                \begin{itemize}
                    \item[] The encoding of the input file. Has priority over --encoding (default: --encoding).
                \end{itemize}
            \item[] --output-encoding: string
                \begin{itemize}
                    \item[] The encoding of the output file. Has priority over --encoding (default: --encoding).
                \end{itemize}
            \item[] --encoding: string
                \begin{itemize}
                    \item[] Encoding of both the input and the output files. Does not have priority (default: UTF-8).
                \end{itemize}
            \item[] --log ou -l: string
                \begin{itemize}
                    \item[] the log level: info, warn or critical (default: critical).
                \end{itemize}
            \item[] --log-file: file
                \begin{itemize}
                    \item[] the file where to log (default: terminal).
                \end{itemize}
        \end{itemize}
\end{itemize}

\end{document}
