\documentclass[manual-fr.tex]{subfiles}
\begin{document}

\begin{itemize}
    \item[] \textbf{description}
        \begin{itemize}
            \item[] Annotate using the annotator passed in argument.
        \end{itemize}
    \item[] \textbf{arguments}
        \begin{itemize}
            \item[] infile
                \begin{itemize}
                    \item[] the input file.
                \end{itemize}
            \item[] outfile
                \begin{itemize}
                    \item[] the output file.
                \end{itemize}
            \item[] annotator
                \begin{itemize}
                    \item[] le name of the annotator.
                \end{itemize}
            \item[] location
                \begin{itemize}
                    \item[] the path where every useful information are to be found (model, folder with lexica, etc).
                \end{itemize}
            \item[] token\_field
                \begin{itemize}
                    \item[] the name of the column where tokens are located (not always useful)
                \end{itemize}
            \item[] field
                \begin{itemize}
                    \item[] the name of the output column
                \end{itemize}
        \end{itemize}
    \item[] \textbf{options}
        \begin{itemize}
            \item[] --help ou -h: switch
                \begin{itemize}
                    \item[] displays help
                \end{itemize}
            \item[] --input-encoding: string
                \begin{itemize}
                    \item[] The encoding of the input file. Has priority over --encoding (default: --encoding).
                \end{itemize}
            \item[] --output-encoding: string
                \begin{itemize}
                    \item[] The encoding of the output file. Has priority over --encoding (default: --encoding).
                \end{itemize}
            \item[] --encoding: string
                \begin{itemize}
                    \item[] Encoding of both the input and the output files. Does not have priority (default: UTF-8).
                \end{itemize}
            \item[] --log ou -l: string
                \begin{itemize}
                    \item[] the log level: info, warn or critical (default: critical).
                \end{itemize}
            \item[] --log-file: file
                \begin{itemize}
                    \item[] the file where to log (default: terminal).
                \end{itemize}
        \end{itemize}
\end{itemize}

\end{document}
